**********
Chapter 1 -- Linear Regression With One Predictor Variable
================================================================================
**********

```{r set-global-opts, include=FALSE}
opts_chunk$set(cache=TRUE, tidy=FALSE)
options(width = 100)
```

Load the data sets
----------------------------------------------------------------------------

```{r}
env <- new.env()                  # Create an environment to store data sets
load("../data.rda", envir = env)  # Load the data sets into this environment
```


Input the Toluca Company Data
----------------------------------------------------------------------------

```{r}
df        <- get("CH01TA01", envir = env)  # Assign a data set to an R object
names(df) <- c("x", "y")                   # Give useful, albeit arbitrary, names to our variables
```


TABLE 1.1     (p 19)
----------------------------------------------------------------------------
#### Data on Lot Size and Work Hours and Needed Calculations for Least Squares Estimates--Toluca Company Example 

```{r}
xx <- scale(df[, 'x'], TRUE, FALSE)  # Center the x values
yy <- scale(df[, 'y'], TRUE, FALSE)  # Center the y values

# Create a table for our output
tab <- transform(df,                 
  x      = x,
  y      = y,
  xdif   = xx,
  ydif   = yy,
  crp    = round(xx * yy),
  sqdevx = xx^2,
  sqdevy = round(yy^2))

# Append summary rows to our table
tab <- rbind(                       
  tab,
  Total = round(apply(tab, 2, sum), 0),
  Mean  = c(colMeans(df), rep("", 5)))

print(tab, quote = FALSE)
```


FIGURE 1.10 and 1.11     (p 20)
----------------------------------------------------------------------------
#### Scatter Plot and Fitted Regression Line--Toluca Company Example Regression Output--Toluca Company Example

```{r}
fit <- lm(y ~ x, data = df)  # Fit the linear regression model
summary(fit)                 # Output summary information for this model

plot(y ~ x, df,  xlab = "Lot Size", ylab = "Hours", pch = 20)
title("(a) Scatter Plot")  # Add a title to the current device plot

# notice the different ways by which to issue plot commands
with(df, plot(x, y, xlab = "Lot Size", ylab = "Hours", pch = 20))
title("(b) Fitted Regression Line")  # Add a title to the current device plot
abline(fit)                          # Add a trend line for this fitted model
```


TABLE 1.2     (p 22)
----------------------------------------------------------------------------
#### Fitted Values, Residuals, and Squared Residuals--Toluca Company Example

Notice the use of "accessor" methods `fitted` and `resid`. They are the recommended way of obtaining fitted values and residuals instead of direct named list element access such as `fit[["residuals"]]`

```{r}
tab <- cbind(
  "Lot Size (X)"       = df$x,
  "Work Hours (Y)"     = df$y,
  "Est. Mean Response" = round(fitted(fit),   2),
  "Residuals"          = round( resid(fit),   2),
  "Sq.Residuals"       = round( resid(fit)^2, 1))

rbind(tab, Totals = colSums(tab))
```
